\Large \bf \projtitle

### 2015-05-05 doc/paper/paper.tex
Add connection manager section

\inclfigure{fig:components}{components.eps}{
    Relationship between different components of the \zbf\ peer-to-peer
    download service. Components in gray are standard browser APIs.
}

@@

>>>>

\inclfigure{fig:components}{components.eps}{
    Relationship between different client-side components of the \zbf\
    peer-to-peer download service. Components in gray are standard browser
    APIs.
}

@@

The connection manager is responsible for establishing connections between
peers and facilitating peer-to-peer message transfers. It is a thin layer on
top of WebRTC that handles maintaining connections with multiple peers,
associating peers with peer IDs that are assigned by our tracker. It manages
all signaling through the signaling channel, which implements signaling through
our central server using WebSockets. At this time, this signaling server is the
same server that is running the tracker, but they are logically separate
components, so theoretically, they could be decoupled if needed for better load
balancing.
